\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-08-22 gwnnDraft02.tex
test
first bit of refs added

The recent experimental detection of gravitational waves~\cite{} gives humanity a new way to observe the universe. Future experiments~\cite{} will greatly expand the frequency range observable. Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{}. Thus searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis.

Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation. This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{}.

>>>>

The recent experimental detection of gravitational waves~\cite{Abbott:2016blz} gives humanity a new way to observe the universe. Future experiments~\cite{Crowder:2005nr,Harry:2006fi,Sathyaprakash:2012jk,2017arXiv170200786A,Seto:2001qf,Sato:2017dkf,Janssen:2014dka} will greatly expand the frequency range observable. Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{Caprini:2015zlo,Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080,Mazumdar:2018dfl}. Thus searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis.

Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation. This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Breitbach:2018ddu}.
